Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-05 tex/VHzQ.tex
VHzQ.tex, VHzQ.pdf update
Bilicki2016 reference added

Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilick2016} found that cross-matches performed with a radius of 2-3'' between the user catalogue and WISE was a good compromise between completeness and contamination \citep[see e.g. Figure 4 of ][]{Krawczyk2013}. We thus use a cross-match radius of 2.75''. When querying the ALLWISE catalogues, ``Cone Search Radius'' in the ALLWISE table search was set to 2.75'' for the Spatial Constraints. The ``One to One Match'' was ``not'' checked; although possible, we consider it highly unlikely there would be more than one MIR source contributing to the flux of a single UV/optically bright rest-frame quasar. Investigating this in detail is very interesting but left to a future study.

@@

\begin{table}
  \centering
  \begin{tabular}{l r r r r}
    \hline \hline
    \multirow{ 2}{*}{$z \geq$} & \multicolumn{2}{c}{unWISE} &  \multicolumn{2}{c}{ALLWISE}   \\ 
                                             & \multicolumn{1}{c}{W1} & \multicolumn{1}{c}{W2} & \multicolumn{1}{c}{W3} & \multicolumn{1}{c}{W4}  \\ 
    \hline
    5.00   &   362 ( 78.2\%)   &   308 ( 66.5\%)  &    51 ( 11.0\%)  &    10 (  2.2\%) \\ 
    5.70   &   186 ( 69.4\%)   &   151 ( 56.3\%)  &    15 (  5.6\%)  &     2 (  0.7\%) \\ 
    6.00   &   109 ( 63.7\%)   &    91 ( 53.2\%)  &     8 (  4.7\%)  &     2 (  1.2\%) \\ 
    6.19   &    63 ( 72.4\%)   &    47 ( 54.0\%)  &     3 (  3.4\%)  &     2 (  2.3\%) \\ 
    6.50   &    34 ( 85.0\%)   &    26 ( 65.0\%)  &     1 (  2.5\%)  &     2 (  5.0\%) \\ 
    6.78   &    12 ( 85.7\%)   &     9 ( 64.3\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.00   &     4 (100.0\%)   &     4 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.50   &     1 (100.0\%)   &     1 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    \hline \line
  \end{tabular}
  \caption{Detection rates in the mid-infrared bands from WISE as a function of 
    redshift. A signal-to-noise cut of {\tt w$x$snr}$>3.0$ has been used for each band.}
  \label{tab:WFCAM_vs_VISTA}
\end{table}

>>>>

Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilicki2016} found that cross-matches performed with a radius of 2-3'' between the user catalogue and WISE was a good compromise between completeness and contamination \citep[see e.g. Figure 4 of ][]{Krawczyk2013}. We thus use a cross-match radius of 2.75''. When querying the ALLWISE catalogues, ``Cone Search Radius'' in the ALLWISE table search was set to 2.75'' for the Spatial Constraints. The ``One to One Match'' was ``not'' checked; although possible, we consider it highly unlikely there would be more than one MIR source contributing to the flux of a single UV/optically bright rest-frame quasar. Investigating this in detail is very interesting but left to a future study.

@@

\begin{table}
  \centering
  \begin{tabular}{l r r r r}
    \hline \hline
    \multirow{ 2}{*}{$z \geq$} & \multicolumn{2}{c}{unWISE} &  \multicolumn{2}{c}{ALLWISE}   \\ 
                                             & \multicolumn{1}{c}{W1} & \multicolumn{1}{c}{W2} & \multicolumn{1}{c}{W3} & \multicolumn{1}{c}{W4}  \\ 
    \hline
    5.00   &   362 ( 78.2\%)   &   308 ( 66.5\%)  &    51 ( 11.0\%)  &    10 (  2.2\%) \\ 
    5.70   &   186 ( 69.4\%)   &   151 ( 56.3\%)  &    15 (  5.6\%)  &     2 (  0.7\%) \\ 
    6.00   &   109 ( 63.7\%)   &    91 ( 53.2\%)  &     8 (  4.7\%)  &     2 (  1.2\%) \\ 
    6.19   &    63 ( 72.4\%)   &    47 ( 54.0\%)  &     3 (  3.4\%)  &     2 (  2.3\%) \\ 
    6.50   &    34 ( 85.0\%)   &    26 ( 65.0\%)  &     1 (  2.5\%)  &     2 (  5.0\%) \\ 
    6.78   &    12 ( 85.7\%)   &     9 ( 64.3\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.00   &     4 (100.0\%)   &     4 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.50   &     1 (100.0\%)   &     1 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    \hline \hline
  \end{tabular}
  \caption{Detection rates in the mid-infrared bands from WISE as a function of 
    redshift. A signal-to-noise cut of {\tt w$x$snr}$>3.0$ has been used for each band.}
  \label{tab:WFCAM_vs_VISTA}
\end{table}
